Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2024-06-19 lqg-strings.tex
added a subsection on discussion about the explicit form of the pullback of the Kalb-Ramond field

>>>>

\subsection{Worldsheet Kalb-Ramond field and Quantum of Area} \label{sec:WS-Kalb-Ramond-QoA}

If one were to calculate the equations of motion for the quantum of area field $\Delta _{a b}$ in the actions \eqref{eqn:modified-NG-action} and \eqref{eqn:inverse-metric-Polyakov} explored in sections \ref{sec:modified-ng} and \ref{sec:inverse-metric-Polyakov}, one would end up concluding that either $\Delta _{a b} = 0$ or it's determinant $\Delta = 0$ vanish. This happens because, as we explored in section \ref{sec:ws-kalb-ramond}, $\Delta _{a b}$ is actually related to the pullback of the Kalb-Ramond field $B_{\mu \nu}$, but those actions were actions for the free string, not coupled to said field. The more complete picture would be thus to consider the string now coupled to the Kalb-Ramond field \cite{Tong2009Lectures}
\begin{multline} \label{eqn:area-corrected-K-R-action}
	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \widetilde{\varepsilon}^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big) ,
\end{multline}
where we can rewrite $\widetilde{\varepsilon}^{a b}$ in terms of $\Delta ^{a b}$ as
\begin{multline} \label{eqn:area-corrected-K-R-action-v2}
	S = - \frac{1}{4 \pi \alpha '} \int \diff ^2 x \left( \sqrt{- g} - \frac{1}{2} \frac{k \Delta}{\sqrt{- g}} \right) \times \\
	\times \Big( g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \sqrt{\Delta} \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Big) .
\end{multline}
By varying this action \wrt $\Delta ^{c d}$ we get
\begin{equation} \label{}
	\Delta _{c d} = \widetilde{f} \del _{c} X^{\mu} \del _{d} X^{\nu} B_{\mu \nu}
\end{equation}
with $\widetilde{f}$ given by
\begin{multline} \label{eqn:1/f-tilde}
	\frac{1}{\widetilde{f}} = \frac{1}{g + \dfrac{k \Delta}{2}} \Bigg( \frac{k \sqrt{\Delta}}{2} g^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu} - \\
	- \left( g + \frac{3 k \Delta}{4} \right) \Delta ^{a b} \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} \Bigg) ,
\end{multline}
where if we take $g_{a b} = \del _{a} X^{\mu} \del _{b} X^{\nu} G_{\mu \nu}$ and $\del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu} = \Delta _{a b} / \widetilde{f}$ this simplifies to
\begin{equation} \label{eqn:f-tilde}
	\widetilde{f} = - \frac{g + k \Delta}{k \sqrt{\Delta}} ,
\end{equation}
from which it is easy to see that the pullback of the Kalb-Ramond field $b_{a b} := \del _{a} X^{\mu} \del _{b} X^{\nu} B_{\mu \nu}$ is given by
\begin{equation} \label{eqn:WS-b-field}
	b_{a b} = - \frac{1}{\dfrac{g}{k \Delta} + 1} \widetilde{\varepsilon}_{a b} ,
\end{equation}
or equivalently that the relation between $\Delta _{a b}$ and $b_{a b}$ is
\begin{equation} \label{eqn:Delta-b-relation}
	\Delta _{a b} = \sqrt{\Delta} \widetilde{\varepsilon}_{a b} = - \sqrt{\Delta} \left( \frac{g}{k \Delta} + 1 \right) b_{a b} .
\end{equation}
